Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2022-03-28 ms.tex
Adjusting content of time-dependent motivation paragraph

>>>>

\textbf{The motivation for including time-dependence in the transfer equation is to characterize the time it takes photons to escape the sphere. This information is needed to calculate the energy deposited into the gas by the scattered photon, which would be necessary for performing radiation hydrodynamics simulations using escape times sampled from this solution. Additionally, steady-state solutions to this problem, while informative, are not always sufficient to describe all the physics of \lya transport. Time-variable, optically-thick environments necessitate a time-dependent solution to include the dynamic effects of \lya transfer. Time-dependent \lya sources include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and sources redshifted by cosmological expansion, which may reveal information about their neutral hydrogen halos and the intergalactic medium \citep{2011MNRAS.418..853X}.}
